\documentclass{article}
\usepackage[utf8]{inputenc}
\synctex=1
\title{Documentation}
\author{tsmoffat}
\date{September 2016}
\usepackage[sfdefault]{FiraSans}
\usepackage{FiraMono}
\usepackage[T1]{fontenc}
\renewcommand*\oldstylenums[1]{{\firaoldstyle#1}}
\usepackage{minted}
\usepackage{hyperref}
\usepackage{geometry}
\newcommand{\q}[1]{``#1''}
\usepackage{tcolorbox}
\usepackage{lineno}

\begin{document}

\maketitle

\section{Introduction}
The aim of this document is to explain the code in the program and how to run it etc. It will be in lieu of comments within the code, due to the large amount of repeated code
within the program

\section{Installation}
To install the program, make sure you have Git installed on your system as well as Git LFS (for large files). Get the URL of the project from GitHub, navigate to
where you would like the project to be stored and run git clone (URL) in your terminal/command line. This will pull the project from GitHub. Then type git lfs track
\q{*.txt} into your terminal to make sure that the large file system is tracking text files, before running git clone (URL) again to download the text files for this program.
\par To run the program, install Anaconda for Python 3.5 from \url{https://www.continuum.io/downloads}. This will make sure that everything is installed correctly. Once this
is installed, restart your terminal then type \q{pip install tabulate} to install the missing package needed for this program.


\section{Running}
There are two options for this. Either navigate to the directory containing the project in your terminal and type Testing2.py
or load the project up in PyCharm and run it from there.

\section{Code Explanation}
This section is intended to explain what the code in the program does, as quite a lot of it is repeated and it saves repeating comments. The self arguments that every function has
refer to global variables and constants.
\subsection{AttenuationSearch.py}
\inputminted[linenos, breaklines]{python}{../AttenuationSearch.py}
This is AttenuationSearch.py. Its purpose is to search through the DSA sheet in the spreadsheet and find the closest attenuation to the input attenuation. The first function,
attlist, just generates a list of all the values present in the DSA sheet, then returns it. It does this by iterating through the column with the S21 values of attenuation,
checking if they have a value, and appending them to the list if they do. The row offset in line 8 is to remove anything that is not a number from the search area.\par The next
function, closest, takes as its argument attlist, which is the list generated in the previous function. It uses a lambda function to find the value with the smallest absolute
distance from the target attenuation, which is called through self.targetatt. This is then converted into a decimal value, as this allows for rounding, unlike a float, and then
returns the value.\par The last function takes as its arguments attlist and closest, and then it iterates through the rows, finding which value is equal to the closest value
then gets the values needed for various other parts of the program from the spreadsheet. All these are then returned in a data dictionary, which is a data type in python that
allows for values to be referenced using a key.
\subsection{extras.py}
\inputminted[linenos, breaklines]{python}{../extras.py}
Extras.py is the multi-use module in this program. The first four functions are used to find if there is a single array answer. These all work in roughly the same way. First, the
looks to see if the target phase is actually present at all in the spreadsheet. If it is then it returns that value, along with the corresponding row and attenuation. Otherwise,
it uses a lambda function to find the closest value in the set (which is like a list but doesn`t allow for duplicate values) and returns the values for that. \par The checkall function
is what controls the previous four functions. It calls them then decides which value to return, by looking to see if any of the returned values equal the target value, and if not finding
the one with the smallest distance. \par The final module in this takes the most accurate values from finding one, two, two, three and four phase answers and then returns the best one.
the way it is laid out, if a value is found with two and three phases, the program will always prefer the more efficient solution (i.e. the one with the fewest phases involved).
\subsection{FourPhase.py}
\inputminted[linenos, breaklines]{python}{../FourPhase.py}
This is FourPhase.py. The first function, closestfinder, finds the closest value to the target value. The line starting \q{combined =} gets the path of the directory where the program
currently is running and then loads the text file specified, before loading it into a set, which ensures there are no duplicate numbers present. The following line uses
a lambda function, which is a function that isn't attached to an identifier, so is only called in that one spot. The purpose of this lambda function is to find the
number with the smallest absolute difference from the target. These two numbers are converted into decimal format, which is like a floating point number but it allows
for rounding, so the number isn't 64 bits. The closest value is then returned to whatever bit of code called it, and is then used later in the program.\par
The other function, check, is an enormous bit of code, but in essence what it does is iterates through the four lists of numbers available to it, s180, s90, s45 and s225,
which correspond to the four spreadsheets of data. It then adds the four numbers together, one from each sheet, and checks to see if the total matches
the closest value from the previous snippet. If the total matches then it it iterates through each sheet in turn, looking for the value of the corresponding
iterator (e.g.it looks for the value of i in the 180 sheet). When it finds this value, it assigns the value of the row (the value in the zeroth column) to row(n),
the value of the attenuation of that phase to att(n), then it works out the difference in phases between the phase at 32GHz and the phase at 24GHz. This is used
in other parts of the program.
\subsection{lookuptablegenerator.py}
\inputminted[linenos, breaklines]{python}{../lookuptablegenerator.py}
This module is supposed to be rarely used. Its purpose is to generate a table of 64 values of either attenuation or phase, and then output them in an easily readable way
using the tabulate module. \par Starting with the tablegen function. This generates sets for the different phases. It then creates a list of the headers used by tabulate.
Then, it starts the main part of the function, where it iterates from 1 to 64 and stores this value in i, before calculating the appropriate multiple of $\frac{-360}{64}$
to be used in this run through the cycle. It then runs in much the same way as the main program (seen later) to get the values of the best results for that attenuation.
Once this has been completed it goes through a very long series of if/else if statements to find the settings to output to the user. The settings themselves are calculated by
taking the row number and formatting it into binary, with various lengths of leading bits. This starts on line 83. The relevant values are added to the table, which is a list
of lists. Once the program has run through 64 times, it prints the table out with nice formatting, and then outputs all the values to a CSV file for easier browsing once the
terminal window has been closed. atttablegen is very similar, it just looks for the attenuation as opposed to the phase.
\subsection{minattvar.py}
\inputminted[linenos, breaklines]{python}{../minattvar.py}
This module searches for the attenuation value with the minimum variation across frequency. It does this by finding the n closest values, n being an integer specified by the
 user, and calling the attenuation search module then using the phase value from calling attenuation search. The attenuation for 24GHz is subtracted from the attenuation for
 32GHz, and then it finds the smallest absolute difference and returns the dictionary with that value in.
 \subsection{mininsertloss.py}
 \inputminted[linenos, breaklines]{python}{../mininsertloss.py}
This module works in much the same way as the previous module, but instead of using AttenuationSearch, it uses FourPhase, and finds the value for the total attenuation from
all four phases, then takes the minimum value out of the n values found.
\subsection{minphaseatt.py}
\inputminted[linenos, breaklines]{python}{../minphaseatt.py}
Another module that works in much the same way as the previous two. In this case it takes the differences in phase across frequency from the DSA sheet and finds the smallest
difference in phase between 24 and 32 GHz.
\subsection{minphasevariation}
\inputminted[linenos, breaklines]{python}{../minphasevariation.py}
This module is the last of the four very similar modules, except in this case it finds the minimum phase variation across frequency by using FourPhase.py and getting the
phases for 24 and 32 GHz before returning the option with the minimum phase variation.
\subsection{Testing2.py}
\inputminted[linenos, breaklines]{python}{../Testing2.py}
This is the main module of the program. The first part, \_\_init\_\_ is where all the global variables are created, most of which are values referring to various columns in
the spreadsheets of data. This is to make remembering values easier. This is also where the sheets themselves are loaded into memory, using openpyxl. The snippet
\mint{python}|os.path.join(os.path.dirname(__file__), `source.xlsx`)|
is a way of getting the absolute path of the file without hard coding it, due to the program not running if the file paths are relative. The main function is what controls
everything else, It starts by getting an input from the user to choose whether they want to generate a table or find a specific value. If they want to find a specific value
then 

\end{document}
